Manuscript figures

### 2024-09-02 manuscript_plots.Rmd
edits for review

## Figure 3
```{r skill-bias-sd}
skill <- 
  temperature_skill |> 
  filter(model_id %in% c(top_mods$model_id) & model_id != 'persistenceRW', 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |> 
  group_by(model_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  mutate(manuscript_name = factor(manuscript_name, levels = levels(model_id_colours$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_crps, colour = manuscript_name)) +
  geom_hline(yintercept = 0, colour = 'grey40' ) + 
  geom_line()  +  
  labs(y='Mean relative skill (°C)', x = 'Horizon (days)') +
  scale_colour_manual(name = 'Model',values = model_id_colours$value) +
  theme_bw()

sd <- temperature_scores |> 
  mutate(horizon = as_date(datetime) - as_date(reference_datetime)) |> 
  filter(model_id %in% top_mods$model_id & model_id != 'persistenceRW',  
         horizon > 0, 
         horizon != 15,
         horizon <=30) |>
  group_by(model_id, horizon) |> 
  summarise(mean_sd = mean(sd, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  mutate(manuscript_name = factor(manuscript_name, levels = levels(model_id_colours$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_sd, colour = manuscript_name)) +
  geom_line()+
  labs(y='Mean standard deviation (°C)', x = 'Horizon (days)') +
  scale_colour_manual(name = 'Model',values = model_id_colours$value) +
  theme_bw()

bias <- temperature_scores |> 
  mutate(horizon = as_date(datetime) - as_date(reference_datetime),
         abs_bias = abs(mean - observation)) |> 
  filter(model_id %in% top_mods$model_id & model_id != 'persistenceRW', 
         horizon > 0, 
         horizon != 15,
         horizon <= 30) |>
  group_by(model_id, horizon) |> 
  summarise(mean_abs_bias = mean(abs_bias, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  mutate(manuscript_name = factor(manuscript_name, levels = levels(model_id_colours$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_abs_bias, colour = manuscript_name)) +
  geom_line()+
  labs(y='Mean absolute bias (°C)', x = 'Horizon (days)') +
  scale_colour_manual(name = 'Model',values = model_id_colours$value) +
  theme_bw() +
  coord_cartesian(ylim = c(0, 2))

@@

good_80 <- 
  plot_reliability(scores = temperature_scores,
                   models = top_mods, # model_ids and manuscript names
                   CI = 80, 
                   order = levels(model_id_colours$manuscript_name)) +
  scale_colour_manual(name = 'Model',values = model_id_colours$value) +
  theme_bw() +
  scale_y_continuous(limits = c(54, 100))

good_95 <- plot_reliability(scores = temperature_scores,
                            models = top_mods, 
                            CI = 95, 
                            order = levels(model_id_colours$manuscript_name)) +
  scale_colour_manual(name = 'Model',values = model_id_colours$value) +
  theme_bw() +
  scale_y_continuous(limits = c(54, 100))

@@

bad_80 <- 
  plot_reliability(scores = temperature_scores,
                 models = bad_mods, 
                 CI = 80, 
                 order = bad_mods$manuscript_name) +
    theme_bw() +
    scale_colour_manual(name = '', values = rep('grey50', 20)) +
    scale_y_continuous(limits = c(0, 100)) + 
    theme(legend.position = 'none')

bad_95 <- plot_reliability(scores = temperature_scores,
                            models = bad_mods, 
                            CI = 95, 
                            order = bad_mods$manuscript_name) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))  +
  scale_colour_manual(name = '', values = rep('grey50', 20))

ggarrange(ggarrange(get_legend(good_80), NULL, nrow = 2),
          ggarrange(good_80, good_95, bad_80, bad_95, align = 'hv', legend= 'none', labels = 'auto'), 
          ncol = 2, 
          widths = c(1,5)) |> 
  ggsave(filename = 'Plots/Figure4.png', height = 17.6, width = 23, units = 'cm')
```

@@

B <- temperature_skill |> 
  filter(model_id %in% top_mods$model_id) |> 
  group_by(site_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  mutate(site_id = factor(site_id, levels = lake_sites)) |> 
  ggplot(aes(x=horizon, 
             y = mean_crps, colour = site_id)) +
  geom_hline(yintercept = 0, colour = 'grey40') + 
  geom_line()  +  
  labs(y='Mean relative skill (°C)', x = 'Horizon (days)') +
  scale_colour_brewer(palette = 'Dark2', name = 'Site')+
  theme_bw()

>>>>

## Figure 3
```{r skill-bias-sd}
skill <- 
  temperature_skill |> 
  filter(model_id %in% c(top_mods$model_id) & model_id != 'persistenceRW', 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |> 
  group_by(model_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  mutate(manuscript_name = factor(manuscript_name, levels = levels(model_id_colours$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_crps, colour = manuscript_name)) +
  geom_hline(yintercept = 0, colour = 'grey40' ) + 
  geom_line(linewidth = 0.8)  +  
  labs(y='Mean relative skill (°C)', x = 'Horizon (days)') +
  scale_colour_manual(name = 'Model',values = model_id_colours$value) +
  theme_bw()

sd <- temperature_scores |> 
  mutate(horizon = as_date(datetime) - as_date(reference_datetime)) |> 
  filter(model_id %in% top_mods$model_id & model_id != 'persistenceRW',  
         horizon > 0, 
         horizon != 15,
         horizon <=30) |>
  group_by(model_id, horizon) |> 
  summarise(mean_sd = mean(sd, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  mutate(manuscript_name = factor(manuscript_name, levels = levels(model_id_colours$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_sd, colour = manuscript_name)) +
  geom_line(linewidth = 0.8)+
  labs(y='Mean standard deviation (°C)', x = 'Horizon (days)') +
  scale_colour_manual(name = 'Model',values = model_id_colours$value) +
  theme_bw()

bias <- temperature_scores |> 
  mutate(horizon = as_date(datetime) - as_date(reference_datetime),
         abs_bias = abs(mean - observation)) |> 
  filter(model_id %in% top_mods$model_id & model_id != 'persistenceRW', 
         horizon > 0, 
         horizon != 15,
         horizon <= 30) |>
  group_by(model_id, horizon) |> 
  summarise(mean_abs_bias = mean(abs_bias, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  mutate(manuscript_name = factor(manuscript_name, levels = levels(model_id_colours$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_abs_bias, colour = manuscript_name)) +
  geom_line(linewidth = 0.8)+
  labs(y='Mean absolute bias (°C)', x = 'Horizon (days)') +
  scale_colour_manual(name = 'Model',values = model_id_colours$value) +
  theme_bw() +
  coord_cartesian(ylim = c(0, 2))

@@

good_80 <- 
  plot_reliability(scores = temperature_scores,
                   models = top_mods, # model_ids and manuscript names
                   CI = 80, 
                   order = levels(model_id_colours$manuscript_name)) +
  scale_colour_manual(name = 'Top model',values = model_id_colours$value) +
  scale_linetype_manual(name = 'Top model',values = model_id_colours$linetype) +
  theme_bw() +
  scale_y_continuous(limits = c(54, 100)) +
  labs(title = 'Top performing models') +
  theme(title = element_text(size = 14))

good_95 <- plot_reliability(scores = temperature_scores,
                            models = top_mods, 
                            CI = 95, 
                            order = levels(model_id_colours$manuscript_name)) +
  scale_colour_manual(name = 'Top model',values = model_id_colours$value) +
  scale_linetype_manual(name = 'Top model',values = model_id_colours$linetype) +
  theme_bw() +
  scale_y_continuous(limits = c(54, 100))

@@

bad_80 <- 
  plot_reliability(scores = temperature_scores,
                   models = bad_mods, 
                   CI = 80, 
                   order = bad_mods$manuscript_name,
                   alpha  = 0.6) +
  theme_bw()  +
  scale_colour_manual(name = '', values = unname(pals::cols25(n= 20)))+ 
  scale_linetype_manual(name = '', values = rep('solid', 20)) +
  theme(legend.position = 'none') +
  labs(title = 'All other submitted models') +
  theme(title = element_text(size = 14))

bad_95 <- plot_reliability(scores = temperature_scores,
                           models = bad_mods, 
                           CI = 95, 
                           order = bad_mods$manuscript_name,
                           alpha  =0.6) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))   +
  scale_colour_manual(name = '', values = unname(pals::cols25(n= 20))) + 
  scale_linetype_manual(name = '', values = rep('solid', 20))

ggarrange(NULL, ggarrange(get_legend(good_80), NULL, nrow = 2),
          ggarrange(good_80, good_95, bad_80, bad_95, align = 'hv', legend= 'none', labels = 'auto', hjust = -4, vjust = 3), 
          ncol = 3, 
          widths = c(0.1,1,5)) |> 
  ggsave(filename = 'Plots/Figure4.png', height = 17.6, width = 23, units = 'cm')
```

@@

lake_order <- temperature_skill |> 
  filter(model_id %in% top_mods$model_id) |> 
  group_by(site_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) %>% 
  filter(horizon == 30) %>% 
  arrange(desc(mean_crps)) %>% 
  pull(site_id)

B <- temperature_skill |> 
  filter(model_id %in% top_mods$model_id) |> 
  group_by(site_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  mutate(site_id = factor(site_id, levels = lake_order)) |> 
  ggplot(aes(x=horizon, 
             y = mean_crps, colour = site_id)) +
  geom_hline(yintercept = 0, colour = 'grey40') + 
  geom_line(linewidth = 0.8)  +  
  labs(y='Mean relative skill (°C)', x = 'Horizon (days)') +
  scale_colour_brewer(palette = 'Dark2', name = 'Site')+
  theme_bw()
